### 2022-01-28 input/experiments.tex
reread and fix some

\subsection{Scalability and trade-off}
\begin{asparadesc}
\item [Objective:] Confirm the scalability of \NAME by higlighting the
  trade-off between the current partitioning of the system and the
  protocol's overhead in terms of generated traffic and termination
  time.

@@

We build a network comprising 10k \processes. First, we chain
\processes together, then we add another communication link per
\process to another random \process. Since links are bidirectional,
each \process has 4 communication links on average. We set the latency
of links between 20 and 40 ms at random following a uniform
distribution.
%
To favor more concurrent operations, we voluntary set
weights and latency to different values: each link has a weight
between 5 and 15 set randomly using a uniform distribution. This
allows nodes to receive messages in a different order than their
respective shortest path generating more messages to reach consistent
partionning.

\noindent To evaluate dynamic consistent partitioning we, first, 
create 100 partitions one at a time: \processes reach consistent
partitioning before we create each new partition. Second, we remove
every partition one at a time, in the order of their creation, hence
starting from the first and oldest partition that had been added.

@@

\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
delete operations are roughly twice as expensive as creation
ones. Indeed, the top part of the figure shows that after 21 seconds,
when the experiment involves removals, traffic includes both
$\alpha$ and $\delta$ messagess. The latter aims at removing stale
information and triggering competition while the former aims at
updating shortest paths. As corollary, the convergence time increases,
for $\delta$ messages must reach the partition borders before sound
competitors propagate their partition. It is worth noting that this
delete operation involves concurrency: removals still propagate while
the competition has started.
%%is already partially triggered and propagating.

\noindent Figure~\ref{fig:complexity} shows that the overhead of
adding the $1^{st}$ partition does not correspond to the overhead of
deleting this $1^{st}$ partition. When adding it, messages must reach
all \processes while when removing it, messages must reach a small
subset of this membership.  \NAME's overhead actually depends on
current partitioning as opposed to past partitionings.

@@

\begin{figure*}
  \subfloat[An infrastructure composed of 40 interconnected autonomous systems and
    1157 \processes spanning across Europe~\cite{knight2011internet}]{
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf} 
  }
  \hspace{5pt}
  \subfloat[Traffic overhead and indexes
    maintained by \NAME and its extension \NAMEC]{
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.pdf}
  }
  \caption{\label{fig:europe-ases} Comparison between \NAME and \NAMEC}
\end{figure*}

@@

\subsection{Cross autonomous systems}
\begin{asparadesc}
\item[Objective:] Highlight the shortcoming of \NAME in
  infrastructures composed of multilple autonomous systems and
    discuss an improvement called \underline{cross} \underline{\NAME}
    (\NAMEC). At coarse-grained, \NAMEC enables
    \emph{lazy}\footnote{Laziness properties and \NAMEC would be
    further detailed in the  additional two pages available in the
    camera-ready version of the article.} dynamic partitioning by
    allowing AS' gateways to stop notifications when their respective
    network does not appear to have a source.

  \item[Description:] We build a network of networks, following the
    GEANT network and the underlying European NRENs.
    Figure~\ref{fig:europe-ases} (a) depicts the resulting
    infrastructure composed of 1157 \processes distributed in 40
    interconnected autonomous systems spanning across
    Europe~\cite{knight2011internet}. \emph{Gateway} \processes (dark
    in the figure) link autonomous systems together, \eg a Lisbon
    \node links Portugal to Spain and United Kingdoms through a Madrid
    \node and a London \node respectively.

    \noindent Figure~\ref{fig:europe-ases} (a) also depicts the
    operations executed during the 7 seconds simulation: at 1 second,
    a \node located in Lisbon, Portugal performs an \texttt{Add} (\ie
    Lisbon becomes a new source); at 2 seconds, a \node located in
    Palma de Majorque, Spain performs an \texttt{Add}; at 3 seconds, a
    \node located in Paris, France performs an \texttt{Add}; at 4
    seconds, a \node located in Hvanneyri, Iceland performs an
    \texttt{Add}; finally at 5 seconds, the \node in Spain performs a
    \texttt{Del} (the Spanish source is removed). Each \node has been
    chosen in order to illustrate the limitation of \NAME and so the
    interest of containning the propagation within an AS as proposed by
    \NAMEC.

    \noindent In \NAMEC, each
    \process maintains a \emph{local} index that corresponds to the
    best partition of its autonomous systems, and a \emph{global}
    index that corresponds to the best partition cross autonomous
    systems, \ie adjacent autonomous systems that have at least one
    source.

@@

  \item[Results:] Figure~\ref{fig:europe-ases} (b) shows the
    results of this experiment. The top part highlights the cost of
    each partitioning protocol after each operation, while the bottom
    part provides the insight that explains these costs by displaying
    the number of indexes maintained by each protocol.

>>>>

\subsection{Scalability and trade-off}
\begin{asparadesc}
\item [Objective:] Confirm the scalability of \NAME by highlighting the
  trade-off between the current partitioning of the system and the
  protocol's overhead in terms of generated traffic and termination
  time.

@@

We build a network comprising 10k \processes. First, we chain
\processes together, then we add another communication link per
\process to another random \process. Since links are bidirectional,
each \process has 4 communication links on average. We set the latency
of links between 20 and 40 ms at random following a uniform
distribution.
%
To favor more concurrent operations, we voluntary set
weights and latency to different values: each link has a weight
between 5 and 15 set randomly using a uniform distribution. This
allows nodes to receive messages in a different order than their
respective shortest path generating more messages to reach consistent
partitioning.

\noindent To evaluate dynamic consistent partitioning, we first
create 100 partitions one at a time: \processes reach consistent
partitioning before we create each new partition. Second, we remove
every partition one at a time, in the order of their creation, hence
starting from the first and oldest partition that had been added.

@@

\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
delete operations are roughly twice as expensive as creation
ones. Indeed, the top part of the figure shows that after 21 seconds,
when the experiment involves removals, traffic includes both
$\alpha$ and $\delta$ messages. The latter aims at removing stale
information and triggering competition while the former aims at
updating shortest paths. As corollary, the convergence time increases,
for $\delta$ messages must reach the partition borders before sound
competitors propagate their partition. It is worth noting that this
delete operation involves concurrency: removals still propagate while
the competition has started.
%%is already partially triggered and propagating.

\noindent Figure~\ref{fig:complexity} shows that the overhead of
adding the $1^{st}$ partition does not correspond to the overhead of
deleting this $1^{st}$ partition. When adding it, messages must reach
all \processes while when removing it, messages must reach a small
subset of this membership.  \NAME's overhead actually depends on
current partitions as opposed to past partitions.

@@

\begin{figure*}
  \subfloat[\label{fig:nrens}Workload in 40 interconnected autonomous systems with
    1157 \processes~\cite{knight2011internet}.]{
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf} 
  }
  \hspace{5pt}
  \subfloat[\label{fig:europe-ases}Traffic overhead and maintained indexes.]{
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.pdf}
  }
  \caption{Limitations of \NAME and evaluation of \NAMEC for lazy dynamic partitioning.}
\end{figure*}

@@

\subsection{Cross autonomous systems}
\begin{asparadesc}
\item[Objective:] Highlight the shortcoming of \NAME in
  infrastructures composed of multiple autonomous systems and
    discuss an improvement called \underline{cross} \underline{\NAME}
    (\NAMEC). At coarse-grained, \NAMEC enables
    \emph{lazy}\footnote{Laziness properties and \NAMEC would be
    further detailed in the  additional two pages available in the
    camera-ready version of the article.} dynamic partitioning by
    allowing AS' gateways to stop notifications when their respective
    network does not appear to have a source.

  \item[Description:] We build a network of networks comprising
    G{\'E}ANT along with the underlying European NRENs.
    Figure~\ref{fig:nrens} depicts the resulting infrastructure
    composed of 1157 \processes distributed in 40 interconnected
    autonomous systems spanning across
    Europe~\cite{knight2011internet}. \emph{Gateway} \processes (dark
    in the figure) link autonomous systems together, \eg a Lisbon
    \node links Portugal to Spain and United Kingdoms through a Madrid
    \node and a London \node respectively.

    \noindent Figure~\ref{fig:nrens} also depicts the
    operations executed during the 7 seconds simulation: at 1 second,
    a \node located in Lisbon, Portugal performs an \texttt{Add}, \ie
    Lisbon becomes a new source; at 2 seconds, a \node located in
    Palma de Majorque, Spain performs an \texttt{Add}; at 3 seconds, a
    \node located in Paris, France performs an \texttt{Add}; at 4
    seconds, a \node located in Hvanneyri, Iceland performs an
    \texttt{Add}; finally at 5 seconds, the \node in Spain performs a
    \texttt{Del}, \ie the Spanish source is removed. We chose each source
    with the aim to illustrate the limitations of \NAME further highlighting
    the interest in containing the propagation within relevant autonomous systems
    as proposed by \NAMEC.

    \noindent In \NAMEC, each
    \process maintains a \emph{local} index that corresponds to the
    best partition of its autonomous system, and a \emph{global}
    index that corresponds to the best partition cross autonomous
    systems, \ie adjacent autonomous systems that have at least one
    source.

@@

  \item[Results:] Figure~\ref{fig:europe-ases} shows the
    results of this experiment. The top part highlights the cost of
    each partitioning protocol after each operation, while the bottom
    part provides the insight that explains these costs by displaying
    the number of indexes maintained by each protocol.

### 2022-01-28 input/proposal.tex
reread and fix some

\begin{definition}[\label{def:forwarding}Forwarding]
  When Node $x$ \underline{f}orwards $f_x(m)$ a message $m$, it
  \underline{s}ends $s_{xy}(m)$ the latter to all its neighbors $y$
  \TODO{enriched} ($\oplus$) with metadata that depends on its local
  knowledge $\sigma_x$:
  $f_x(m) \implies \forall \langle x, y\rangle \in E: s_{xy}(m
  \TODO{\oplus} \sigma_x)$.
\end{definition}

>>>>

\begin{definition}[\label{def:forwarding}Forwarding]
  When Node $x$ \underline{f}orwards $f_x(m)$ a message $m$, it
  \underline{s}ends it ($s_{xy}(m)$) to all its neighbors $y$
  accumulating and aggregating ($\oplus$) metadata that depends on its
  local knowledge $\sigma_x$: $f_x(m) \implies \forall \langle x,
  y\rangle \in E: s_{xy}(m \oplus \sigma_x)$.
\end{definition}

### 2022-01-28 input/related_work.tex
reread and fix some

\noindent The most closely related approaches to \NAME come from
\underline{i}nformation-\underline{c}entric \underline{n}etworking
(ICN)~\cite{garcia-lopez, hemmati2015namebased} and distributed
clustering~\cite{sohier2012physarum}. The sources advertise themselves
periodically. Advertisements either stop as soon as they reach
uninterested \processes~\cite{garcia-lopez, hemmati2015namebased}, or
probabilistically propagate through most likely interested
\processes~\cite{sohier2012physarum}. However their operation requires
that
\begin{inparaenum}[(i)]
\item they constantly generate traffic even in quiescent systems where
  \processes do not add nor destroy replicas; and 
\item they either operate in synchronous
  systems~\cite{sohier2012physarum} or must define
  physical-clock-based timeouts the value of which depends on network
  topology properties such as network diameter~\cite{garcia-lopez,
    hemmati2015namebased}.
  %also incur an overhead even in quiet contexts without any update.
  % Moreover, they necessarily rely on physical timeouts
  Unfitting timeouts lead to premature removals of live replicas; or
  slow convergence where \processes wrongly believe that their closest
  replica is live while it was destroyed.
\end{inparaenum}
On the opposite, \NAME quickly informs each \process of its closest
replica even in large and dynamic networks with asynchronous
communications; and has no overhead when the system is quiescent.

>>>>

\noindent The most closely related approaches to \NAME come from
\underline{i}nformation-\underline{c}entric \underline{n}etworking
(ICN)~\cite{garcia-lopez, hemmati2015namebased} and distributed
clustering~\cite{sohier2012physarum}. The sources advertise themselves
periodically. Advertisements either stop as soon as they reach
uninterested \processes~\cite{garcia-lopez, hemmati2015namebased}, or
propagate through most likely interested
\processes~\cite{sohier2012physarum}. However their operation requires
that
\begin{inparaenum}[(i)]
\item they constantly generate traffic even in quiescent systems where
  \processes do not add nor destroy replicas; and 
\item they either operate in synchronous
  systems~\cite{sohier2012physarum} or must define
  physical-clock-based timeouts the value of which depends on network
  topology properties such as network diameter~\cite{garcia-lopez,
    hemmati2015namebased}.
  %also incur an overhead even in quiet contexts without any update.
  % Moreover, they necessarily rely on physical timeouts
  Unfitting timeouts lead to premature removals of live replicas; or
  slow convergence where \processes wrongly believe that their closest
  replica is live while it was destroyed.
\end{inparaenum}
On the opposite, \NAME quickly informs each \process of its closest
replica even in large and dynamic networks with asynchronous
communications; and has no overhead when the system is quiescent.
